Graph Convolution Networks

### 2017-08-31 Work_report/Presentation/GCN/gcn_presentation.tex
Done a little more, need to add quantitative and qualitative results
Possibly some pictures

\begin{frame}
  \frametitle{Graph Laplacian (contd.)}
  $$\mathcal{L} = T^{-1/2}LT^{1/2}$$
  With the convention $T^{-1}(v,v) = 0$ for $d_v = 0$.\\
  When G is k-regular,
  $$\mathcal{L} = I - \frac{1}{k}A$$
  For a general graph
  $$\mathcal{L} = I - T^{-1/2}AT^{1/2}$$
\end{frame}

@@

>>>>

\begin{frame}
  \frametitle{Graph Laplacian (contd.)}
  $$\mathcal{L} = T^{-1/2}LT^{1/2}$$
  With the convention $T^{-1}(v,v) = 0$ for $d_v = 0$.\\
  When G is k-regular,
  $$\mathcal{L} = I - \frac{1}{k}A$$
  For a general graph
  $$\mathcal{L} = I - T^{-1/2}AT^{1/2}$$
\end{frame}
\section{Spectral Networks and Deep Locally Connected Networks on Graphs}
\begin{frame}
  \frame{Spectral Network Approach}
  \begin{itemize}
  \item Mentions the use of both spatial and spectral construction.
  \item For the spectral part uses a spline and has k control points for it.
    $$g_{\theta}(\Lambda) = B\theta$$
    Here $B$ is the cubic B-spline basis and $\theta$ is a vector of control points.
  \item The datasets used (created) are quite interesting. Subsampled MNIST and MNIST on sphere to show how spectral networks can be used on graphs.
  \end{itemize}
\end{frame}

@@

\subsection{Coarsening and Pooling}
\begin{frame}
  \frametitle{Graph Coarsening and Pooling}
  \begin{itemize}
  \item Require efficient mechanism for pooling. Graph clustering as such is NP-hard and some approximations must be made.
  \item The paper uses Graclus algorithm for coarsening, and uses an intelligent way of rearranging the nodes [creating a balanced binary tree from the remaining singleton and fake nodes] so that the pooling now becomes equivalent to pooling a regular 1D signal.
  \end{itemize}
\end{frame}

\subsection{Results on MNIST}
\begin{frame}
  \frametitle{MNIST results}
  \begin{itemize}
  \item Achieves close to classical CNN accuracy.
  \item Pictures to be added.
  \end{itemize}
\end{frame}
